---
title: "CO2 Report"
author: "Desiree Vera"
date: "2022-12-08"
output: html_document
runtime: shiny
resource_files:
- app_ui.R
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction
Co2 emissions and their contribution to climate change have been a topic of
discussion, measure and comparison for decades. Different countries, depending
on their level of per capita income have taken strides in decreasing their emissions,
especially while still increasing their yearly GDP. Other countries are less
wealthy, but still focussed on growing GDP and potentially less focused on their
carbon footprint. For this reason I wanted to look into CO2 emissions per 1 unit
of GDP. I found that in the emissions data collected over the course of 271 years,
leading up to 2021. Kuwait had the highest measured CO2 emissions per unit of GDP
many other countries were listed as having no emissions due to no data being collected on them.
The average CO2 per gdp across the dataset was 0.42.


```{r eruptions, echo=FALSE}
source("app_server.R")
source("app_ui")
source("app.R")
# Define content for the second page
co2_page <- tabPanel(
  "CO2 per GDP",
  selectizeInput("Country", "Select Country", co2_per_gdp$country, selected = NULL,
                 multiple = TRUE)
)
co2_vis <- selectInput(
  inputId = "country",
  label = "Select A Country",
  choices = co2_per_gdp$country,
  selected = NULL
)
description <- sidebarPanel(co2_page, co2_vis, 
                            print("Looking at the countries with the highest emissions per dollar of GDP shows which are not doing enough to combat emissions."))

plot_on_page <- mainPanel(
  plotlyOutput(co2_plot)
)
# Pass each page to a multi-page layout (`navbarPage`)
ui <- navbarPage(
  "Exploring CO2 Emitted per dollar of GDP", # application title
  intro,         # include the first page content
  co2_page,         # include the second page content
)

```




